On the performance of the MAC model

### 2018-11-01 2018_nips_vigil/appendix.tex

Most of the VQA datasets contain ambiguities and have strong linguistic biases that allow a model to learn answering strategies that exploit those biases, without reasoning about the visual input ~\cite{Santoro2017ASN}
The CLEVR dataset ~\cite{johnson2017clevr}  was developed to address those issues and come back to the core challenge of visual QA which is reasoning  \href{url}{https://arxiv.org/pdf/1612.06890.pdf}.\\
CLEVR contains images of 3D-rendered objects, such as spheres and cylinders. Each image is associated with a number of questions that fall into different categories. For example, query attribute questions may ask “What is the color of the sphere?”, while compare attribute questions may ask “Is the cube the same material as the cylinder? ”.
The dataset consist of:
\begin{itemize}
\item 	A training set of 70k images and 700k questions
\item	A test  set of 15k images and 150k questions about objects
\item	A validation set of 15k images and 150k 
\item	Answers, scene graphs and functional programs for all train and val images and questions

>>>>

Most of the VQA datasets contain ambiguities and have strong linguistic biases that allow a model to learn answering strategies that exploit those biases, without reasoning about the visual input ~\cite{Santoro2017ASN}
The CLEVR dataset ~\cite{johnson2017clevr}  was developed to address those issues and come back to the core challenge of visual QA which is reasoning  \href{url}{https://arxiv.org/pdf/1612.06890.pdf}.\\
CLEVR contains images of 3D-rendered objects, such as spheres and cylinders. Each image is associated with a number of questions that fall into different categories. For example, query attribute questions may ask “What is the color of the sphere?”, while compare attribute questions may ask "Is the cube the same material as the cylinder? ”.
The dataset consist of:
\begin{itemize}
\item 	A training set of 70k images and 700k questions
\item	A test  set of 15k images and 150k questions about objects
\item	A validation set of 15k images and 150k 
\item	Answers, scene graphs and functional programs for all train and val images and questions

### 2018-11-01 2018_nips_vigil/conclusion.tex

\section{Conclusion}
We have introduced SMAC, a simplified version on the MAC model. This version has simplified equations and therefore we could reduce significantly the number of parameters in the MAC cell, which is the recurrent unit of the model. As a result we could decrease training time by more than two hours while maintaining an equivalent test accuracy. 
We have also put to test the MAC and SMAC models on a novel task, the CLEVR CoGenT dataset.
It is a structured dataset especially designed to study transfer learning and generalization abilities. The results of our experiments first show that MAC and SMAC perform equally well on all the CoGenT task. Thus the simplifications did not alter SMAC generalization capability.
Furthermore, MAC and SMAC compare favorably with state-of-the-art models on the CoGenT taks. MAC and SMAC present competitive generalization and transfer learning capacities.
Nevertheless, CLEVR CoGenT remains an unsolved problem. The MAC model still struggles to learn distinct concepts. We could see that MAC sometimes fail to differentiate colors and shape as two distinct features of the same object.

+ Ppening on future work
+ Tomasz’s comment on finetuning

>>>>

\section{Conclusion}
We have introduced SMAC, a simplified version on the MAC model. This version proposes simplified equations and therefore we could reduce significantly the number of parameters in the MAC cell, which is the recurrent unit of the model. As a result we could decrease training time by more than two hours ( reduction by almost 10 \%)
while maintaining an equivalent test accuracy. 
We have also put to test the MAC and SMAC models on a novel task, the CLEVR CoGenT dataset.
It is a structured dataset especially designed to study transfer learning and generalization abilities. The results of our experiments first show that MAC and SMAC perform equally well on all the CoGenT task. Thus the simplifications did not alter SMAC generalization capability.
Furthermore, MAC and SMAC compare favorably with state-of-the-art models on the CoGenT taks. MAC and SMAC present competitive generalization and transfer learning capacities.
Nevertheless, CLEVR CoGenT remains an unsolved problem. The MAC model still struggles to learn distinct concepts. We could see that MAC sometimes fail to differentiate colors and shape as two distinct features of the same object.

+ Opening on future work/ideas
+ Tomasz’s comment on finetuning
